---
output: rmarkdown::github_document
---

`msgxtractr` : Read Outlook '.msg' Files

A 'reticulate' wrapper to the Python 'ExtractMessage' module.

### IMPORTANT FIRST STEP

Users need Python installed and either do:

    pip install https://github.com/mattgwwalker/msg-extractor/zipball/master

or

    pip3 install https://github.com/mattgwwalker/msg-extractor/zipball/master

from the command-line depending on which version of python you have.

### TODO

- Attachments

The following functions are implemented:

- `read_msg`	Read an Outlook '.msg' file into a data frame

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/msgxtractr")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(msgxtractr)

# current verison
packageVersion("msgxtractr")

dplyr::glimpse(read_msg(system.file("extdata/unicode.msg", package="msgxtractr")))
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(msgxtractr)
library(testthat)

date()

test_dir("tests/")
```

